---
title: "Introduction to SC19077"
author: "Shan Pang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19077}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19077__ is a simple R package developed to give the estimations of parameters of the mixture of two normal distributions by two methods which are MLE and EM algorithms.

## Estimation by MLE

```{r}
mixnormal2 <- function(x,initial,data){
  LL <- function(params, data=data) { 
    t1 <- dnorm(data, params[2], params[3])
    t2 <- dnorm(data, params[4], params[5])
    f <- params[1] * t1 + (1 - params[1]) * t2
    ll <- sum(log(f))
    return(-ll)
  }
  res <- nlminb(initial,LL,
                data=data,
                lower=c(.00001,-Inf,.00001,-Inf,.00001),
                upper=c(0.99999,Inf,Inf,Inf,Inf))
  y <- res$par[1]*dnorm(x,res$par[2],res$par[3])+(1-res$par[1])*dnorm(x,res$par[4],res$par[5])
  return(y)
}
```
  
  
LL is the log-likelihood function of the data. Then we use function $nlminb()$ to get the estimates of parameters. The function $nlminb()$ has three inputs, which are $initial$ indicating the initial values of the parameters, $LL$ indicating the log-likelihood function and $data$ indicating the data we are going to use for MLE. Since $nlminb()$ is to minize $LL$, we set $LL$ as the opposite of log-likelihood.  

An example is showed below:

```{r}
n <- 200
u <- runif(n)
x <- ifelse(u<.7,rnorm(n),rnorm(n,3,9))
mixnormal2(0.8,c(.65,-0.1,1.59,3.21,7.99),x)
```
  
  
  
## Estimation by EM algorithms

```{r}
gmm <- function(p,mu,sig,data){
  n <- length(data)
  dat <- matrix(rep(data,2),ncol=2,byrow=F)
  prob <- matrix(0,nrow=n,ncol=2)
  
  while(TRUE){
    for(i in 1:2)
      prob[,i] <- as.matrix(sapply(dat[,i],dnorm,mu[i],sig[i]))
    pmatrix <- matrix(rep(p,n),ncol=2,byrow=T)
    a <- pmatrix*prob
    b <- matrix(rep(rowSums(a),2),ncol=2)
    w <- a/b
    
    oldp <- p
    oldmu <- mu
    oldsig <- sig

    p <- colSums(w)/n
    mu <- colSums(dat*w)/colSums(w) 
    d <- matrix(rep(mu,n),ncol=2,byrow=T)
    sig <- colSums(w*(dat-d)^2)/colSums(w)

    if((sum((p-oldp)^2) < 1e-4) &
       (sum((mu-oldmu)^2) < 1e-4) &
       (sum((sig-oldsig)^2) < 1e-4) )break
  }
  return(list(p=p,mu=mu,sig=sig))
}
```
  
  
Actually, there are sealed function to implement EM algorithms. But here we review the EM algorithm through this funciton $gmm()$. In E-step we calculate the probabilities of each sample generated from each normal distribution. In M-step we generate new values of parameters which assure the log-likelihood function is growing bigger. Replace the old values of parameters by new one until the residuals between old values and new values are smaller than the setting threshold.  


An example is showed below:

```{r}
n <- 200
u <- runif(n)
x <- ifelse(u<.7,rnorm(n),rnorm(n,3,9))
gmm(c(0.65,0.35),c(-0.1,3.21),c(1.59,7.99),x)
```



#### Homeworks 
# title: "A-19077-2018-09-20"
## 1.Text 
### Something about statistical computing class

Q:Why do you take statistical computing class?  
A:I hope to excell in programming with R and contribute my own packages on the Internet although my programming skill is somehow weak now.

Q:What do you think of statistical computing?  
A:Statistical computing is interesting! The tools that teacher talked about in the class are so advanced and convinient that I can not wait using them!

Q:How do you improve your programming skill?  
A:I prepare to practice programming everyday and read codes online.

## 2.Table
### Make my own curriculum schedule

```{r}
library(knitr)
num <- 1:5
Mon <- c(' ',' ','English',' ','Politcs')
Tues <- c(' ',' ','Probability',' ',' ')
Wed <- c('Linear Model',' ',' ',' ',' ')
Thur <- c('Probability',' ',' ',' ',' ')
Fri <- c(' ','Computing','Linear Model',' ',' ')
schedule <- data.frame(num,Mon,Tues,Wed,Thur,Fri)
kable(schedule)
```


## 3.Figure
### LDA for iris data set
 
```{r}
library(MASS)
attach(iris)
train <- sample.int(150,100)
fit <- lda(Species~.,iris[train,])
plot(fit,main="QDA for iris Dataset")
``` 



```{r}
sigma <- 1:4 
f1 <- function(x){
x/(sigma[1]^2)*exp(-x^2/(2*sigma[1]^2))}

f2 <- function(x){
x/(sigma[2]^2)*exp(-x^2/(2*sigma[2]^2))}

f3 <- function(x){
x/(sigma[3]^2)*exp(-x^2/(2*sigma[3]^2))}

f4 <- function(x){
x/(sigma[4]^2)*exp(-x^2/(2*sigma[4]^2))}
t <- seq(0,10,0.01)
curve(f1,0,10)
curve(f2,0,10)
curve(f3,0,10)
curve(f4,0,10)
```

```{r}
set.seed(1)
n <- 1e2
rn <- matrix(rep(0,n*4),ncol=4)

i <- c(0,0,0,0) 
j <- c(0,0,0,0) 

for(k in 1:4){

  while(i[k]<n){
  u <- runif(1) 
  j[k] <- j[k]+1
  x <- rgamma(1,shape=2,scale=2*sigma[k]^2)
  
   if(u <= exp((x-x^2)/(2*sigma[k]^2))){
    i[k] <- i[k]+1
    rn[i[k],k] <- x
   }
  
  }
  
}
j
i
```

```{r}

hist(rn[,1],prob=T,xlab='x',ylab='f(x)',main=expression(f(x)==x/sigma[1]^2*e^(-x^2/2*sigma[1]^2)))
lines(t,f1(t))

hist(rn[,2],prob=T,xlab='x',ylab='f(x)',main=expression(f(x)==x/sigma[2]^2*e^(-x^2/2*sigma[2]^2)))
lines(t,f2(t))

hist(rn[,3],prob=T,xlab='x',ylab='f(x)',main=expression(f(x)==x/sigma[3]^2*e^(-x^2/2*sigma[3]^2)))
lines(t,f3(t))

hist(rn[,4],prob=T,xlab='x',ylab='f(x)',main=expression(f(x)==x/sigma[4]^2*e^(-x^2/2*sigma[4]^2)))
lines(t,f4(t))

```

The histograms above show that the mode of the 4 groups of generated samples are all close to the corresponding theoretical mode.

  


### Question 2 ###

Generate a random sample of size 1000 from a normal location mixture. The components of the mixture have N(0, 1) and N(3, 1) distributions with mixing probabilities p1 and p2 = 1 − p1. Graph the histogram of the sample with density superimposed, for p1 = 0.75. Repeat with different values for p1 and observe whether the empirical distribution of the mixture appears to be bimodal. Make a conjecture about the values of p1 that produce bimodal mixtures.

### Answer ###

First,generate random sample from the specified normal location mixture with $p_1=0.75$.Then graph the histogram of the sample.  
    
```{r}
set.seed(2)
n <- 1e3
u <- runif(n)
rn <- ifelse(u<.75,rnorm(n),rnorm(n,3,1))
t <- seq(-6,6,.01)
hist(rn,prob=T,xlim=c(-6,6),ylim=c(0,0.4),main='Normal Location Mixtrue of N(0,1) and N(3,1) for p1=0.75')
lines(t,0.75*dnorm(t,0,1)+0.25*dnorm(t,3,1))
```

Graph the histograms of samples for $19$ different $p_1$ which ranges from $0.05$ to $0.95$.

```{r}
p1 <- seq(.05,.95,.05) 
mix <- matrix(rep(0,n*19),ncol=19)

for(i in 1:19){
  u <- runif(n)
  mix[,i] <- ifelse(u<p1[i],rnorm(n),rnorm(n,3,1))
}

x <- seq(-4,8,.01)
for(i in 1:19){
  p <- 0.05*i
  hist(mix[,i],prob=T,xlim=c(-4,8),ylim=c(0,0.5),main='')
  legend(5,0.5,title="p1",p,xjust=0,box.lty = 0)
 lines(x,p1[i]*dnorm(x,0,1)+(1-p1[i])*dnorm(x,3,1))
}
```


```{r echo=T}
rmvn <- function(d,n,Sigma){
  
  T <- matrix(rep(0,d*d),nrow=d)
  for(i in 1:d){
   x <- rchisq(1,n-i+1)
   T[i,i] <- sqrt(x)
  }
  for(i in 2:d){
   for(j in 1:(i-1) ){
      T[i,j] <- rnorm(1)
   }
  }
  A <- T %*% t(T)
  
  ev <- eigen(Sigma)
  lambda <- ev$values
  v <- ev$vectors

  L <- v %*% diag(sqrt(lambda)) %*% t(v)
  
  rn <- L %*% A %*% t(L)
  
}

```


Let's do simulation.

```{r echo=T}
n <- 5
d <- 3
B <- matrix(c(1,1,1,1,2,4,1,3,9),nrow=3)
Sigma <- (B/10) %*% t(B/10)
Sigma
r <- rmvn(d,n,Sigma)
r
```

The random sample $r$ above is generated from $W_3(\sum ,5)$,where $\sum =$ 
$$
\begin{bmatrix}
0.03&0.06&0.14\\
0.06&0.14&0.36\\
0.14&0.36&0.98
\end{bmatrix}
$$
```{r}
real <- cos(0) - cos(pi/3)
real

set.seed(1)
n <- 1e4
x <- runif(n,0,pi/3)
theta <- round(mean(pi/3*sin(x)),5)
theta <- real 
```

```{r}
set.seed(4)
g <- function(x){pi/3*sin(x)}
f <-function(x){pi/3*x}

n <- 1e4
r <- 1e3
u <- runif(r,0,pi/3)
c <- -cov(f(u),g(u))/var(f(u))
c

MC1 <- MC2 <- numeric(n)
for (i in 1:n){
  v <- runif(r,0,pi/3)
  MC1[i] <- mean(g(v))
  MC2[i] <- mean(g(v)+c*(f(v)-pi/3*pi/6))
}
theta1 <- mean(MC1)
theta2 <- mean(MC2)
theta1
theta2
(var(MC1)-var(MC2))/var(MC1)
```

```{r}
set.seed(2)

g <- function(x){exp(-x)/(1+x^2)}
n <- 1e3
r <- 1e4

MC1 <- MC2 <- numeric(n)
for (i in 1:n){
  u <- runif(r/2)
  v <- runif(r/2)
  MC1[i] <- round(mean(g(c(u,v))),5)
  MC2[i] <- round(mean(g(c(u,1-u))),5)
}
alpha1 <- round(mean(MC1),5)
alpha2 <- round(mean(MC2),5)
alpha1
alpha2
(var(MC1)-var(MC2))/var(MC1)
```
```{r}
set.seed(3)
k <- 5
Finvers <- function(x){-log(1-(1-exp(-1))*x)}
a <- c(rep(0,5),1)
for (i in 2:5){
  a[i] <- Finvers((i-1)/5)
}
a
```
We get 5 subintervals:$[0,0.135),[0.135,0.291),[0.291,0.477),[0.477,0.705),[0.705,1]$.

```{r}
n <- 100
r <- 100
g <- function(x){exp(-x)/(1+x^2) * (x>0) * (x<1)}
f <- function(x){exp(-x)/(1-exp(-1))}
p <- function(x){k*f(x)}
Ginvers <- function(a,u){-log(exp(-a)-(1-exp(-1))/5*u)}

theta <- numeric(n)
b <- numeric(k)
for (i in 1:n){
  for (j in 1:k){
    u <- runif(r/k,a[j],a[j+1])
    x <- Ginvers(a[j],u)
    b[j] <- mean( g(x)/p(x) * (x>a[j]) * (x<a[j+1]) )
  }
  theta[i] <- sum(b)
}
round(mean(theta),5)

se <- 0.0970314
(se^2 - var(theta))/se^2
```
```{r}
set.seed(1)
m <- 1e4
n <- 20
alpha <- .05
UCL <- LCL <- numeric(m)
for (i in 1:m){
  x <-  rchisq(n,2)
  UCL[i]=mean(x)+var(x)/sqrt(n)*qt(alpha/2,df=n-1,lower.tail = F)
  LCL[i]=mean(x)-var(x)/sqrt(n)*qt(alpha/2,df=n-1,lower.tail = F)
}
r <- mean(LCL < 2 & 2 < UCL)
r
abs(r - (1-alpha)) - abs(0.956 - (1-alpha))
se <- sqrt(r*(1-r)/m)
se
(0.00689 - se)/0.00689
```
```{r,eval=TRUE}
set.seed(2) 
m <- 100
a <- 1e3
n <- 50
q <- c(.025,.05,.95,.975)
xq <- qnorm(q,0,sqrt(6/n))

sk <- function(x){
  xbar <- mean(x)
  m3 <- mean((x-xbar)^3)
  m2 <- mean((x-xbar)^2)
  return(m3/m2^1.5)
}
 
b <- numeric(a)
for(j in 1:a){
    x <- rnorm(n)
    b[j] <- sk(x)
  }
M <- quantile(b,q)

for (i in 1:(m-1)){
   for(j in 1:a){
      x <- rnorm(n)
      b[j] <- sk(x)
   }
   r <- quantile(b,q)
   M <- rbind(M,r)
}

xq.est <- apply(M,2,mean)
se.xq.est <- apply(M,2,sd)
t <- dnorm(xq,0,sqrt(6*(n-2)/((n+1)*(n+3))))
se <- sqrt( q*(1-q)/n/t^2 )
knitr::kable(rbind(xq,xq.est), formate = "html",col.names = c(".025",".05","0.95","0.975"))
knitr::kable(rbind(se,se.xq.est), formate = "html",col.names = c(".025",".05","0.95","0.975"))
```
```{r}
set.seed(1)
alpha <- .05
a <- 1
b <- 10
dis <- seq(0,1,.05)
m <- 1e4
n <- 30
cv <- qnorm(1-alpha/2,0,sqrt(6*(n-2)/(n+1)/(n+3)))
pwr1 <- numeric(length(dis))
sk <- function(x){
  xbar <- mean(x)
  return(mean((x-xbar)^3)/(mean((x-xbar)^2))^1.5)
}

for(i in 1:length(dis)){
  d <- dis[i]
  sktest <- numeric(m)
  for(j in 1:m){
   u <- runif(n)
   x <- ifelse(u<d, rbeta(n,a,a),rbeta(n,b,b))
    sktest[j] <- as.integer(abs(sk(x)) >= cv)
  }
 pwr1[i] <- mean(sktest) 
}
plot(dis,pwr1,type="b",xlab="d",ylab="power",main="Power of skewness test against Beta(a,a)")
abline(h=alpha,lty = 3)
```
    
  In order to calculate power of the skewness test against symmetric Beta distribution, we get different samples from $H_1$ by setting $d$ ranging from 0 to 1.   
  The figure above shows that the power rises firstly and then goes down as $d$ increases and reaches the peak when $d$ is 0.1 or so. Morever,the power is bigger than $\alpha$ when $d < 0.4$ and smaller than $\alpha$ when $d > 0.4$. In general, the power of skewness test of normality against symmetric Beta distribution is no bigger than 0.4 which means the skewness test of normality against $Beta(\alpha,\alpha)$ isn't very good. 

  
(2) The skewness test of normality with sampling distribution $t(v)$  
    We sample from $H_1$ by choosing a contaminated t distribution $d t(v_1) + (1-d)t(v_2)$ where $v_1\neq v_2$.

```{r}
set.seed(2)
alpha <- .05
t1 <- 2
t2 <- 9#parameter of beta distribution
dis <- seq(0,1,.05)#probabilities to sample
m <- 1e4
n <- 30
cv <- qnorm(1-alpha/2,0,sqrt(6*(n-2)/(n+1)/(n+3)))
pwr2 <- numeric(length(dis))
sk <- function(x){
  xbar <- mean(x)
  return(mean((x-xbar)^3)/(mean((x-xbar)^2))^1.5)
}

for(i in 1:length(dis)){
  d <- dis[i]
  sktest <- numeric(m)
  for(j in 1:m){
   u <- runif(n)
   x <- ifelse(u<d, rt(n,t1),rt(n,t2))
   sktest[j] <- as.integer(abs(sk(x)) >= cv)
  }
 pwr2[i] <- mean(sktest) 
}
plot(dis,pwr2,type="b",xlab="d",ylab="power",main="Power of skewness test against t(v)")
abline(h=alpha,lty=3)
```


From the figure above we can see the empirical power of skewness test against t distribution is increasing with the increasement of $d$ and are almost all bigger than those of symmetric Beta distribution. This implies that sampling from t-distribution is better than from symmetric Beta in order to calculate the power of skewness test of normality.
```{r}
set.seed(3)
alpha <- .05
mu0 <- 1
n <- seq(20,500,30)
m <- 100
p.hat <- numeric(length(n))
for(i in 1:length(n)){
  N <- n[i]
  ttest <- numeric(m)
  for(j in 1:m){
    x <- rchisq(N,1)
    ttest[j] <- t.test(x,mu = mu0)$p.value
  }
  p.hat[i] <- mean(ttest <= alpha)
}
se <- sqrt(p.hat*(1-p.hat)/m)

plot(n,p.hat,ylab="tIe",type="b",pch=20)
abline(h=alpha,lty=3)
lines(n, p.hat+se ,lty=3)
lines(n,p.hat-se, lty=3)
```


The figure shows that you'd better choose lage n for t test against $\chi^2(1)$ in order to get a close approximation to $\alpha$. But the empirical type I error of t test against $\chi^2(1)$ is almost all bigger than $\alpha$.


(2) t-test against $U(0,2)$
 
```{r}
set.seed(4)
alpha <- .05
mu0 <- 1
n <- seq(20,500,30)
m <- 100
p.hat <- numeric(length(n))
for(i in 1:length(n)){
  N <- n[i]
  ttest <- numeric(m)
  for(j in 1:m){
    x <- runif(N,0,2)
    ttest[j] <- t.test(x,mu = mu0)$p.value
  }
  p.hat[i] <- mean(ttest <= alpha)
}
se <- sqrt(p.hat*(1-p.hat)/m)

plot(n,p.hat,ylab="tIe",type="b",pch=20)
abline(h=alpha,lty=3)
lines(n, p.hat+se ,lty=3)
lines(n,p.hat-se, lty=3)
```
```{r}
set.seed(6)
alpha <- .05
mu0 <- 1
n <- seq(20,500,30)
m <- 100
p.hat <- numeric(length(n))
for(i in 1:length(n)){
  N <- n[i]
  ttest <- numeric(m)
  for(j in 1:m){
    x <- rexp(N,1)
    ttest[j] <- t.test(x,mu = mu0)$p.value
  }
  p.hat[i] <- mean(ttest <= alpha)
}
se <- sqrt(p.hat*(1-p.hat)/m)

plot(n,p.hat,ylab="tIe",type="b",pch=20)
abline(h=alpha,lty=3)
lines(n, p.hat+se ,lty=3)
lines(n,p.hat-se, lty=3)
```


The figure shows that you'd better choose $n>100$ for t test against $E(1)$ in order to get a close approximation to $\alpha$.
Comparing to (2),the empirical type I error may be smaller than $alpha$ slightly sometimes in (3).


#### Question 3 ####
If we obtain the powers for two methods under a particular simulation setting with 10000 experiements:say,0.651 for one method and 0.676 for another.Can we say the powers are different at 0.05 level?
```{r}
set.seed(7)
n <- 30
m <- 100
p1 <- 0.651
p2 <- 0.676
x <- rbinom(n,size=m,prob=p1)
y <- rbinom(n,size=m,prob=p2)
ttest <- t.test(x,y,conf.level = alpha)
p <- ttest$p.value
p
```


From the result of t test, we should reject $H_0$ indicating that we can't say the powers are the same at 0.05 level


---
title: "A-19077-2019-11-08"
author: "By-19077"
date: "2019/11/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Question 1 ####
Efron and Tibshirani discuss the scor (bootstrap) test score data on 88 students who took examinations in five subjects [84, Table 7.1], [188, Table 1.2.1].
The first two tests (mechanics, vectors) were closed book and the last three
tests (algebra, analysis, statistics) were open book. Each row of the data
frame is a set of scores (xi1, . . . , xi5) for the ith student. Use a panel display
to display the scatter plots for each pair of test scores. Compare the plot with
the sample correlation matrix. Obtain bootstrap estimates of the standard
errors for each of the following estimates: ˆ ρ12 = ˆ ρ(mec, vec), ˆ ρ34 = ˆ ρ(alg,
ana), ˆ ρ35 = ˆ ρ(alg, sta), ˆ ρ45 = ˆ ρ(ana, sta)

#### Answer 1 ####

1) panel display

```{r,results = "hide"}
library(bootstrap)
data(scor)
attach(scor)
pairs(scor,labels=c("mec","vec","alg","ana","sta"))
round(cor(scor),4)
```
```{r}
set.seed(1)
library(boot)
n <- nrow(scor)
r <- 100
f12 <- function(x,i)cor(x[i,1],x[i,2])
f34 <- function(x,i)cor(x[i,3],x[i,4])
f35 <- function(x,i)cor(x[i,3],x[i,5])
f45 <- function(x,i)cor(x[i,4],x[i,5])
cor12 <- boot(data=scor, statistic=f12, R=r)
cor34 <- boot(data=scor, statistic=f34, R=r)
cor35 <- boot(data=scor, statistic=f35, R=r)
cor45 <- boot(data=scor, statistic=f45, R=r)
boot.est <- cbind(cor12[1],cor34[1],cor35[1],cor45[1])
boot.est <- round(as.numeric(boot.est),3)
y <- cbind(cor12$t,cor34$t,cor35$t,cor45$t)
se.hat <- round(apply(y,2,sd),4)
f = data.frame(boot.est,se.hat,row.names=c("rho12","rho34","rho35","rho45"))
knitr::kable(f)
```
```{r,results = "hide"}
set.seed(2)
n <- 20
m <- 100
sk1 <- 0

library(boot)
sk <- function(x) {
  xbar <- mean(x)
  m3 <- mean((x - xbar)^3)
  m2 <- mean((x - xbar)^2)
  return( m3 / m2^1.5 )
}
b <- function(x,i)sk(x[i])

n.ci.norm <- n.ci.basic <- n.ci.perc <- matrix(NA,m,2)
n.cover <- n.misleft <- n.misright <- numeric(3)

for (i in 1:m){
   x <- rnorm(n)
   n.boot.est <- boot(data=x,statistic=b,R=m)
   n.boot.ci <- boot.ci(n.boot.est,type=c("norm","basic","perc"))
   n.ci.norm[i,] <- n.boot.ci$normal[2:3]
   n.ci.basic[i,] <- n.boot.ci$basic[4:5]
   n.ci.perc[i,] <- n.boot.ci$percent[4:5]
 } 

n.norm.indic <- n.basic.indic <- n.perc.indic <- numeric(m)
n.norm.left <- n.norm.right <- numeric(m)
n.basic.left <- n.basic.right <- numeric(m)
n.perc.left <- n.perc.right <- numeric(m)
for (i in 1:m){
  n.norm.indic[i] <- as.integer(n.ci.norm[i,1] <=  0 & 0 <= n.ci.norm[i,2])
  n.basic.indic[i] <- as.integer(n.ci.basic[i,1] <= 0 & 0 <= n.ci.basic[i,2])
  n.perc.indic[i] <- as.integer(n.ci.perc[i,1] <= 0 & 0 <= n.ci.perc[i,2])
  n.norm.right[i] <- as.integer(n.ci.norm[i,2] < 0)
  n.basic.right[i] <- as.integer(n.ci.basic[i,2] < 0)
  n.perc.right[i] <- as.integer(n.ci.perc[i,2] < 0)
  n.norm.left[i] <- as.integer(0 < n.ci.norm[i,1] )
  n.basic.left[i] <- as.integer(0 < n.ci.basic[i,1])
  n.perc.left[i] <- as.integer(0 < n.ci.perc[i,1])
}
n.cover <- c(mean(n.norm.indic),mean(n.basic.indic),mean(n.perc.indic))
n.misleft <- c(mean(n.norm.left),mean(n.basic.left),mean(n.perc.left))
n.misright <- c(mean(n.norm.right),mean(n.basic.right),mean(n.perc.right))
n.cover
n.misright
n.misleft
```

```{r,results = "hide"}
set.seed(3)
n <- 20
m <- 100

f <- function(x){dchisq(x,5)*(x-5)^3/sqrt(10)^3}
sk2 <- round(integrate(f,0,Inf)$value,3)
sk2

ch.ci.norm <- ch.ci.basic <- ch.ci.perc <- matrix(NA,m,2)
ch.cover <- ch.misleft <- ch.misright <- numeric(3)

for (i in 1:m){
   x <- rchisq(n,5)
   ch.boot.est <- boot(data=x,statistic=b,R=m)
   ch.boot.ci <- boot.ci(ch.boot.est,type=c("norm","basic","perc"))
   ch.ci.norm[i,] <- ch.boot.ci$normal[2:3]
   ch.ci.basic[i,] <- ch.boot.ci$basic[4:5]
   ch.ci.perc[i,] <- ch.boot.ci$percent[4:5]
 } 

ch.norm.indic <- ch.basic.indic <- ch.perc.indic <- numeric(m)
ch.norm.left <- ch.norm.right <- numeric(m)
ch.basic.left <- ch.basic.right <- numeric(m)
ch.perc.left <- ch.perc.right <- numeric(m)
for (i in 1:m){
  ch.norm.indic[i] <- as.integer(ch.ci.norm[i,1] <=  sk2 & sk2 <= ch.ci.norm[i,2])
  ch.basic.indic[i] <- as.integer(ch.ci.basic[i,1] <= sk2 & sk2 <= ch.ci.basic[i,2])
  ch.perc.indic[i] <- as.integer(ch.ci.perc[i,1] <= sk2 & sk2 <= ch.ci.perc[i,2])
  ch.norm.right[i] <- as.integer(ch.ci.norm[i,2] < sk2)
  ch.basic.right[i] <- as.integer(ch.ci.basic[i,2] < sk2)
  ch.perc.right[i] <- as.integer(ch.ci.perc[i,2] < sk2)
  ch.norm.left[i] <- as.integer(sk2 < ch.ci.norm[i,1] )
  ch.basic.left[i] <- as.integer(sk2 < ch.ci.basic[i,1])
  ch.perc.left[i] <- as.integer(sk2 < ch.ci.perc[i,1])
}
ch.cover <- c(mean(ch.norm.indic),mean(ch.basic.indic),mean(ch.perc.indic)) 
ch.misleft <- c(mean(ch.norm.left),mean(ch.basic.left),mean(ch.perc.left)) 
ch.misright <- c(mean(ch.norm.right),mean(ch.basic.right),mean(ch.perc.right)) 
ch.cover #0.719 0.702 0.71
ch.misright #0.26 0.264 0.29
ch.misleft #0.021 0.034    0
```

From the above we have the coverage rates of normal distribution and $\chi^2(5)$ are

```{r,echo=FALSE,eval=TRUE}
f <- data.frame(n.cover,ch.cover,row.names=c("Standard","Basic","Percentile"))
knitr::kable(f)
```

The rates of missing on the right and on the left of normal distribution are

```{r,echo=FALSE,eval=TRUE}
f <- data.frame(n.misright,n.misleft,row.names=c("Standard","Basic","Percentile"))
knitr::kable(f)
```

The rates of missing on the right and on the left of $\chi^2(5)$ distribution are

```{r,echo=FALSE,eval=TRUE}
f <- data.frame(ch.misright,ch.misleft,row.names=c("Standard","Basic","Percentile"))
knitr::kable(f)
```
```{r}
library(bootstrap)
n <- nrow(scor)
cov1 <- (n-1)/n*cov(scor)
value1 <- unlist(eigen(cov1, symmetric=T, only.values=T))
theta.hat <- max(value1)/sum(value1)

theta.jack <- numeric(n)
for (i in 1:n){
  cov2 <- (n-1)/n*cov(scor[-i,])
  value2 <- unlist(eigen(cov2, symmetric=T, only.values=T))
  theta.jack[i] <- max(value2)/sum(value2)
}

bias.jack <- (n-1)*(mean(theta.jack) - theta.hat)
se.jack <- sqrt( (n-1) * mean( (theta.jack - mean(theta.jack))^2 ))
bias.jack <- round(bias.jack,5)
se.jack <- round(se.jack,4)
print(c(bias = bias.jack,se = se.jack))
```


## Question 2: T7.10,P213
In Example 7.18, leave-one-out (n-fold) cross validation was used to select the best fitting model. Repeat the analysis replacing the Log-Log model with a cubic polynomial model. Which of the four models is selected by the cross validation procedure? Which model is selected according to maximum adjusted R2?

```{r}
library(DAAG)
attach(ironslag)
modl <- c("Linear","Quadratic","Exponential","CubicPolynomial")

which.best <- function(dat){
  n <- length(dat[,1])
  
  y1 <- y2 <- y3 <- y4 <- numeric(n)
  for (i in 1:n){
    x <- dat[-i,1]
    y <- dat[-i,2]
    x0 <- dat[i,1]
    
    cv1 <- lm( y ~ x )
    a1 <- cv1$coef
    y1[i] <- a1[1] + a1[2]*x0
    
    cv2 <- lm( y ~ x + I(x^2))
    a2 <- cv2$coef
    y2[i] <- a2[1] + a2[2]*x0 + a2[3]*x0^2
    
    cv3 <- lm( log(y) ~ x)
    a3 <- cv3$coef
    y3[i] <- exp( a3[1] + a3[2]*x0 )
   
    cv4 <- lm( y ~ poly(x,degree=3))
    a4 <- cv4$coef
    y4[i] <- a4[1] + a4[2]*x0 + a4[3]*x0^2 + a4[4]*x0^3
  }
  y <- cbind(y1,y2,y3,y4)
  
  Y <- dat[,2]
  e <- numeric(4)
  for (i in 1:4)e[i] <- mean((Y-y[,i])^2)
  
  SST <- sum((Y - mean(Y))^2)
  SSR <- numeric(4)
  for (i in 1:4)SSR[i] <- sum((Y-y[,i])^2)
  k <- c(1,2,1,3)
  R2 <- SSR/SST
  adjR2 <- (1-(1-R2))*(n-1)/(n-k-1)
  
  num <- c(which.min(e),which.max(adjR2))
  return(c(CrossValidation=modl[num[1]],adjustedR2=modl[num[2]]))
}

which.best(ironslag)
```



The empirical Type I error rate is 0.044 which demonstrates that critical value of 6 is better than 5 in this issue with unequal sample sizes.


---
title: "A-19077-2019-11-29"
author: "By 19077"
date: "2019/11/29"
output: html_document
---


#### Question: T9.3,P277
Implement a random walk Metropolis sampler for generating the standard
Laplace distribution $f(x)={1\over2}e^{-|x|}$(see Exercise 3.2). For the 
increment, simulate from a normal distribution. Compare the chains generated
when different variances are used for the proposal distribution. Also,
compute the acceptance rates of each chain.


#### Answer 

Implement the random walk version of the Metropolis sampler to generate the
target standard Laplace distribution, using the proposal distribution Normal($Xt$, $\sigma^2$).


```{r}
library(GeneralizedHyperbolic)
rw.Metropolis <- function(x0,N,sigma){
  x <- numeric(N)
  x[1] <- x0
  u <- runif(N)
  k <- 0
  for (i in 2:N){
    y <- rnorm(1,x[i-1],sigma)
    if (u[i] <= dskewlap(y) / dskewlap(x[i-1]))
      x[i] <- y
    else{
      x[i] <- x[i-1]
      k <- k+1
      
    }
  }
  return(list(x=x,k=k))
}

sigma <- c(.05,.1,seq(.2,1,.4),seq(2,6,1),10)
n <- length(sigma)
N <- 2000
x0 <- rnorm(1)
rw <- matrix(nrow=N,ncol=n)
Num_of_Reject <- numeric(n)
for (i in 1:n){
 rw[,i] <- rw.Metropolis(x0,N,sigma[i])$x
 Num_of_Reject[i] <- rw.Metropolis(x0,N,sigma[i])$k
}
```


The acceptance rate is as follows:

```{r}
Accept_Rate <- round(1-Num_of_Reject/N,3)
knitr::kable(rbind(Num_of_Reject,Accept_Rate),formate="html",col.names=c("0.05","0.1","0.2","0.6","1","2","3","4","5","6","10"))

refline <- qskewlap(c(.025,.975))
for (i in 1:n){
  plot(1:N,rw[,i],type="l",xlab=bquote(sigma==.(sigma[i])),ylab="X")
  abline(h=refline)
}

```

From the figures above we can see:  
a)the chains didn't converge when $\sigma < 0.6$;  
b)when $\sigma > 2$ there are many short horizontal paths in the graph in which the candidate point is rejected and the chain didn't move at these time points.

In conclusion, if we want to implement a random walk Metropolis sampler for generating the standard Laplace distribution with normal proposal distribution, we'd better choose standard deviation with $0.6 \leq \sigma \leq2$.


---
title: "A-19077-2019-12-06"
author: "By 19077"
date: "2019/12/10"
output:
  html_document: default
---


### Question 1:T11.1,P353
The natural logarithm and exponential functions are inverses of each other,
so that mathematically log(exp x) = exp(log x) = x. Show by example that
this property does not hold exactly in computer arithmetic. Does the identity
hold with near equality? (See all.equal.)

### Answer1

```{r}
isTRUE(exp(log(.001))==.001)
isTRUE(log(exp(.001))==.001)
isTRUE(log(exp(.001))==exp(log(.001)))

isTRUE(all.equal(log(exp(.001)),.001))
isTRUE(all.equal(exp(log(.001)),.001))
isTRUE(all.equal(exp(log(.001)),log(exp(.001))))
```
  In the example above I choose $x=0.001$. And $e^{ln(0.001)}$ and $ln e^{0.001}$ should be the same in the mathematical calculation but not in the computer arithmetic. Hence the function "isTRUE" returned "FALSE". However, with near equality the identity holds and the function "isTRUE" with "all.equal" returned "TRUE".

### Quesion 2:T11.5,P355
> Write a function to solve the equation $$\frac{2\Gamma\left(\frac{k}{2}\right)}{\sqrt{\pi(k-1)}\Gamma\left(\frac{k-1}{2}\right)}\int_{0}^{c_{k-1}}\left(1+\frac{u^{2}}{k-1}\right)^{-k/2}du =\frac{2\Gamma\left(\frac{k+1}{2}\right)}{\sqrt{\pi k}\Gamma\left(\frac{k}{2}\right)} \int_{0}^{c_{k}}\left(1+\frac{u^{2}}{k}\right)^{-(k+1)/2}du  
$$ 
for a, where $c_{k}=\sqrt{\frac{a^{2} k}{k+1-a^{2}}}$. Compare the solutions with the points $A(k)$ in Exercise 11.4.
$$

```{r}
#####11.4
K <- c(4:25,100,500,1e3)
UP <- sqrt(K)
n <- length(K)
A <- numeric(n)

for (i in 1:n){
  k <- K[i]
  f <- function(a){
   pt(sqrt(a^2*(k-1)/(k-a^2)),k-1) - pt(sqrt(a^2*k/(k+1-a^2)),k)
  }
  a <- UP[i]/2+1
  out <- uniroot(f,c(0.5,a))
  A[i] <- out$root
}

```



```{r}
### 11.5
K1 <- c(4:25,100)
n1 <- length(K1)
B <- numeric(n1)

ck <- function(k,a)sqrt((k*(a^2))/(k+1-a^2))
integ_f1 <- function(u)(1+(u^2)/(k-1))^(-k/2)
integ_f2 <- function(u)(1+(u^2)/k)^((-1-k)/2)

f <- function(a){
gamma(k/2)/(gamma((k-1)/2)*sqrt(k-1))*integrate(integ_f1,0,ck(k-1,a))$value-gamma((k+1)/2)/(gamma(k/2)*sqrt(k))*integrate(integ_f2,0,ck(k,a))$value
}

for (i in 1:n1){
  k <- K1[i]
  B[i] <- uniroot(f,lower=0.05,upper=(sqrt(k)/2+1))$root
}
```

```{r}
A <- round(A[1:n1],4)
B <- round(B,4)
err <- A-B

f <- data.frame(rbind(A,B,err),row.names=c("11.4","11.5","error"))
knitr::kable(f)
```

### Question 3
> Let the three alleles be A, B, and O with allele frequencies p, q, and r. The 6 genotype frequencies under HWE and complete counts are as follows.

|Genotype |AA| BB |OO| AO| BO| AB| Sum |
|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|
|Frequency | $p^2$ |$q^2$| $r^2$| 2pr| 2qr| 2pq |1 |
|Count| $n_{AA}$ |$n_{BB}$ |$n_{OO}$ |$n_{AO}$| $n_{BO}$| $n_{AB}$| n|

+ Observed data: 
   + $n_{A·}=n_{AA}+n_{AO}$=28(A-type), 
   + $n_{B·}=n_{BB}+n_{BO}$=24(B-type), 
   + $n_{OO}$=41(O-type), 
   + $n_{AB}$=70(AB-type). 
+ Use EM algorithm to solve MLE of p and q (consider missing data $n_{AA}$ and $n_{BB}$). 
+ Show that the log-maximum likelihood values in M-steps are increasing via line plot.

### Answer 3

```{r}
library(rootSolve)
r <- 1e3
n1 <- 28
n2 <- 24
n3 <- 41
n4 <- 70
p0 <- .1
q0 <- .1
L <- c(.1,.1)
tol <- .Machine$double.eps^0.5
L.old <- L+1
logML <- numeric(r)
for(j in 1:r){
  logML[j] <- 2*p0*n1*log(p0)/(2-p0-2*q0)+2*q0*n2*log(q0)/(2-q0-2*p0)+2*n3*log(1-p0-q0)+n1*(2-2*p0-2*q0)*log(2*p0*(1-p0-q0))/(2-p0-2*q0)+n2*(2-2*p0-2*q0)*log(2*q0*(1-p0-q0))/(2-q0-2*p0)+n4*log(2*p0*q0)
  g <- function(x){
    F1 <- 2*p0*n1/((2-p0-2*q0)*x[1])-2*n3/(1-x[1]-x[2])+n1*(2-2*p0-2*q0)*(1-2*x[1]-x[2])/((2-p0-2*q0)*x[1]*(1-x[1]-x[2]))-n2*(2-2*p0-2*q0)/((2-q0-2*p0)*(1-x[1]-x[2]))+n4/x[1]
    F2 <- 2*q0*n2/((2-q0-2*p0)*x[2])-2*n3/(1-x[1]-x[2])-n1*(2-2*p0-2*q0)/((2-p0-2*q0)*(1-x[1]-x[2]))+n2*(2-2*p0-2*q0)*(1-2*x[2]-x[1])/((2-q0-2*p0)*x[2]*(1-x[1]-x[2]))+n4/x[2]
    c(F1=F1,F2=F2)
  }
  ss=multiroot(f=g,star=c(.1,.1))
  L=ss$root
  if (sum(abs(L-L.old)/L.old)<tol) break
  L.old <- L
}
L.old
plot(logML,type = "l")

```


---
title: "A-19077-2019-12-13"
author: "By 19077"
date: "2019/12/13"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1:AR,P204,T3

Use both for loops and lapply() to fit linear models to the
mtcars using the formulas stored in this list:
formulas <- list(
mpg ~ disp,
mpg ~ I(1 / disp),
mpg ~ disp + wt,
mpg ~ I(1 / disp) + wt
)

### Answer 1

```{r}
attach(mtcars)
formulas <- list(
  mpg ~ disp,
  mpg ~ I(1 / disp),
  mpg ~ disp + wt,
  mpg ~ I(1 / disp) + wt
)

#lapply
##version 1
lm_result1 <- lapply(formulas,function(x)lm(x))
##version 2
lm_result1 <- lapply(formulas,lm,data=mtcars)

#for
lm_result2 <- vector("list",length(formulas))
for (i in seq_along(formulas))lm_result2[[i]] <- lm(formulas[[i]])

#coefficients
l_int <- round(sapply(lm_result1,function(x)x$coefficients[1]),3)
l_coef <- round(sapply(lm_result1,function(x)x$coefficients[2]),3)
f_int <- round(sapply(lm_result2,function(x)x$coefficients[1]),3)
f_coef <- round(sapply(lm_result2,function(x)x$coefficients[2]),3)

```

### Question 2:AR,P204,T4

Fit the model mpg ~ disp to each of the bootstrap replicates
of mtcars in the list below by using a for loop and lapply().
Can you do it without an anonymous function?
bootstraps <- lapply(1:10, function(i) {
rows <- sample(1:nrow(mtcars), rep = TRUE)
mtcars[rows, ]
})

### Answer 2

```{r}
attach(mtcars)
bootstraps <- lapply(1:10, function(i) {
  rows <- sample(1:nrow(mtcars), rep = TRUE)
  mtcars[rows, ]
})

#for
results1 <- vector("list",length(bootstraps))
for(i in seq_along(bootstraps)){
  mt <- bootstraps[[i]]
  results1[[i]] <- lm(mt[,1]~mt[,3])
}

#lapply
results2 <- lapply(bootstraps,function(x)lm(x[,1]~x[,3]))

#coefficients
f_intercpt <- f_coef <- numeric(length(results1))
for(i in seq_along(bootstraps)){
  f_intercpt[i] <- results1[[i]]$coefficients[1]
  f_coef[i] <- results1[[i]]$coefficients[2]
}
round(f_intercpt,3)
round(f_coef,3)
```


```{r}
#without anonymous function
results4 <- lapply(bootstraps,lm,formula=mpg~disp)
```

### Question 3:AR,P204,T5

For each model in the previous two exercises, extract R2 using
the function below.
rsq <- function(mod) summary(mod)$r.squared

### Answer 3

```{r}
rsq <- function(mod) summary(mod)$r.squared

#T3
t3 <- sapply(lm_result1,rsq)
round(t3,3)
```

```{r}
#T4
t4 <- sapply(results1,rsq)
round(t4,3)
```


### Question 4:AR,P214,T3

The following code simulates the performance of a t-test for
non-normal data. Use sapply() and an anonymous function
to extract the p-value from every trial.
trials <- replicate(100,t.test(rpois(10, 10), rpois(7, 10)),simplify = FALSE)
Extra challenge: get rid of the anonymous function by using [[ directly.

### Answer 4

```{r}
trials <- replicate(100,t.test(rpois(10, 10), rpois(7, 10)),simplify = FALSE)
p_result1 <- sapply(trials,function(x)x$p.value)
round(p_result1[1:10],3)
```

```{r}
p_result2 <- sapply(trials,"[[","p.value")
round(p_result2[1:10],3)
```

### Question 5:AR,P214,T7

Implement mcsapply(), a multicore version of sapply(). Can you implement mcvapply(), a parallel version of vapply()? Why or why not?

### Answer 5

```{r}
library(parallel)
cores <- detectCores(logical = FALSE)
cl <- makeCluster(getOption("cl.cores", cores))
parSapply(cl, 1:500, get("+"), 3)[1:10]
```

  
   As for whether we can implement a parallel version of vapply(), my answer is NO. The condition for parallelisation is that each iteration is isolated from all others(See P212,Advanced R),that is when we scrambl the order of elements of X and iterate in sequence, the answer is always the same.  
   
   To make this clear, we can see the explanation code of lapply() in Advanced R:
   
```{r}
lapply2 <- function(x, f, ...) {
  out <- vector("list", length(x))
  for (i in seq_along(x))out[[i]] <- f(x[[i]], ...)
  out
}
```

  When we scramble the order of computation, the explanation code of apply() becomes:(caution:the order of computation changes because of function "sample")
  
```{r}
lapply3 <- function(x, f, ...) {
  out <- vector("list", length(x))
  for (i in sample(seq_along(x)))out[[i]] <- f(x[[i]], ...)
  out
}
```

However, the result is the same as before so lapply() has its parallel mclapply(). So is function slapply().  

But for vapply(), the example below shows that when the order of computation changes, the result of vapply() may be changed.

```{r}
x <- 1:10
y <- rep("a",10)
df1 <- data.frame(x,y)
df2 <- data.frame(y,x)
vapply(df1,class,FUN.VALUE=character(1))
vapply(df2,class,FUN.VALUE=character(1))
```

The result changes so vapply() can't have its parallelisation mcvapply().


---
title: "A-19077-2019-12-20"
author: "By 19077"
date: "2019/12/20"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

### Question  

(1) You have already written an R function for Exercise 9.4 (page 277, Statistical Computing with R).Rewrite an Rcpp function for the same task.  

9.4 Implement a random walk Metropolis sampler for generating the standard
Laplace distribution (see Exercise 3.2). For the increment, simulate from a
normal distribution. Compare the chains generated when different variances
are used for the proposal distribution. Also, compute the acceptance rates of
each chain.


```{r}
## r
library(GeneralizedHyperbolic)
rw.Metropolis <- function(x0,N,sigma){
  x <- numeric(N)
  x[1] <- x0
  u <- runif(N)
  k <- 0
  for (i in 2:N){
    y <- rnorm(1,x[i-1],sigma)
    if (u[i] <= dskewlap(y) / dskewlap(x[i-1]))
      x[i] <- y
    else{
      x[i] <- x[i-1]
      k <- k+1
    }
  }
  return(list(x=x,k=k))
}
```

```{r}
## C++
library(Rcpp)

### generate random numbers
cppFunction('NumericVector rwMetropolisC(double x0, int N, double sigma){
  NumericVector xC(N);
  xC[0] = x0;
  NumericVector u = runif(N);
  int k = 0;
  for(int i = 1; i < N; i++) {
    double y = (rnorm(1,xC[i-1],sigma))[0];
    double res = exp(abs(xC[i-1]) - abs(y));
    if(u[i] < res){
      xC[i] = y;
    }
    else{
      xC[i] = xC[i-1];
      k ++;}
    };
  return xC;}')

### generate k
cppFunction('int rw_k_C(double x0, int N, double sigma){
  NumericVector xC(N);
  xC[0] = x0;
  NumericVector u = runif(N);
  int k = 0;
  for(int i = 1; i < N; i++) {
    double y = (rnorm(1,xC[i-1],sigma))[0];
    double res = exp(abs(xC[i-1]) - abs(y));
    if(u[i] < res){
      xC[i] = y;
    }
    else{
      xC[i] = xC[i-1];
      k ++;}
    };
  return k;}')
```


(2) Compare the generated random numbers by the two functions using qqplot.

```{r}
rw.Metropolis <- function(x0,N,sigma){
  x <- numeric(N)
  x[1] <- x0
  u <- runif(N)
  k <- 0
  for (i in 2:N){
    y <- rnorm(1,x[i-1],sigma)
    if (u[i] <= dskewlap(y) / dskewlap(x[i-1]))
      x[i] <- y
    else{
      x[i] <- x[i-1]
      k <- k+1
    }
  }
  return(list(x=x,k=k))
}

sigma <- c(.1,.5,2,5,10)
n <- length(sigma)
N <- 2000
x0 <- rnorm(1)
rwM <- matrix(nrow=N,ncol=n)
rwM_C <- matrix(nrow=N,ncol=n)
Num_of_Reject <- numeric(n)
Num_of_Reject_C <- numeric(n)
for (i in 1:n){
 rwM[,i] <- rw.Metropolis(x0,N,sigma[i])$x
 Num_of_Reject[i] <- rw.Metropolis(x0,N,sigma[i])$k
 rwM_C[,i] <- rwMetropolisC(x0,N,sigma[i])
 Num_of_Reject_C[i] <- rw_k_C(x0,N,sigma[i])
}
Accept_rate_R <- round(1-Num_of_Reject/N,3)
Accept_rate_Cpp <- round(1-Num_of_Reject_C/N,3)

#compare random numbers
qqplot(rwM, rwM_C, xlab = deparse(substitute(rwM)),ylab = deparse(substitute(rwM_C)),main="rwMetropolis with R and Cpp",col="blue")
x <- seq(-6,6,.05)
lines(x,x,col="red")

#compare accept rate
knitr::kable(rbind(Accept_rate_R,Accept_rate_Cpp),formate="html",col.names=c("0.1","0.5","2","5","10"))

```


(3) Campare the computation time of the two functions with
microbenchmark.


```{r}
library(microbenchmark)
ts <- list(n)
for (i in 1:n){
 times <- microbenchmark(rwM=rw.Metropolis(x0,N,sigma[i])$x,
 rwM_C=rwMetropolisC(x0,N,sigma[i]))
 ts[[i]] <- summary(times)[,c(1,3,5,6)]
}
ts
```
             
From the qqplot we can see that the random numbers generated from R and C++ respectively are approximately lining near the line $y=x$ which indicates that these two groups of data are from the same distribution.  

The times generating two groups of data by R and C++ respectively are significantly different. C++ spends 66 times less than R in average.



